\documentclass[10pt,one-side,a4paper]{memoir}
\pagestyle{empty}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
%\renewcommand{\chaptername}{}
%\renewcommand{\thechapter}{}
\let\footruleskip\undefined
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhead{}
\fancyfoot{}
\lhead{\textsf{MS23: Milestone Report for Task 5.4 (Dynamic Tape-archive extraction and post-processing)}}
\rhead{\thepage}
\setsecnumdepth{subsubsection}
\setcounter{tocdepth}{3}
\renewcommand*\thesection{\arabic{section}}
\begin{document}
\setlength{\parindent}{0mm}
\begin{center}
\Huge{\textbf{MS23: Milestone Report for Task 5.4 \\(Dynamic Tape-archive extraction and post-processing)}}
\end{center}
The task will be targeting access to tape archive datasets from the MARS tape archive at LIU as well as at the MOHC tape archive at the UK MetOffice. 
\section{MARS tape archive at LIU}
\subsection{Organizations}
LIU/NSC \& SMHI
\subsection{Progress till date}
\begin{enumerate}
\item The system to be developed for the purpose of publishing offline data from MARS onto ESGF and enabling their retrieval has been titled `System for Offline Data Access (SODA)'. 
\item The architecture diagram for SODA has been created and distribution of tasks completed. 
\item SODA is a system based on the Web Processing Service (WPS) with support for plugins, to allow use of backend systems other than MARS.  
\item The components of SODA would be the following:
\begin{enumerate}
\item SODA WPS: interacted with by ESGF WebFE/CoG and SODA-generated wget script.
\item Backend Plugin aka MARS plugin
\item SODA Publisher: script to obtain data questionnaire from SODA WPS and perform insertion into ESGF database and other tasks to complete `ESGF publication'.
\item SODA Scheduler: to schedule publication requests and downloads requests.
\item SODA Messenger: to email notifications
\item SODA file server: for online hosting of requested files.
\end{enumerate}

\item SODA has been discussed and presented at three workshops:
\begin{enumerate}
\item Workshop at ECMWF, Reading UK (CLIPC WP5 workshop)
\item \href{http://www.clipc.eu/portal-design-workshop/content=0055_000000}{Workshop at KNMI, Netherlands (Workshop on design of scientific portals)}
\item \href{http://esgf.llnl.gov/facetoface.html}{ESGF Face2Face meeting, Livermore CA, USA}
\end{enumerate}
\item Feedback was received from the above presentations and incorporated into design revisions.
\item A common Data Reference Syntax (DRS) and mapping document for EURO4M data is being worked upon by SMHI.
\item Communication has been initiated with ESGF developers to work out the integration of SODA with ESGF.
\item Effort has been put into stuyding the process of GRIB to NetCDF conversion, and the work has been presented at the \href{http://www.clipc.eu/portal-design-workshop/content=0055_000000}{`Closing the GRIB/NetCDF gap' workshop at ECMWF}
\end{enumerate}
\subsection{Future work}
Work will now move to actual development of code modules. A skeletonized  version of the implementation is planned to allow for iterative development and testing of components in a sandbox-like environment. Once code is ready, help would be sought to integrate SODA with ESGF.

\subsection{Attachments}
Please refer to the following documents for additional information:
\begin{enumerate}
\item System for Offline Data Access (SODA), a presentation on SODA.
\item Developer notes for CLIPC/ESGF integration
\end{enumerate}
%\newpage
%\begin{center}
%\Huge{\textbf{MS23: Milestone Report by Mark Elkington \\(For reference)}}
%\end{center}
%\begin{center}
%\Huge{\textbf{MS23: Milestone Report for Task 5.4 \\(Dynamic Tape-archive extraction and post-processing)}}
%\end{center}
\section{MOHC tape archive at the UK MetOffice}
\subsection{Organizations}
MOHC \& STFC
\subsection{Progress till date}
MOHC attended the work package workshop in Reading during September. Since then MOHC and BADC staff have held regular
meetings to establish an architectural design for a BADC interface to climate data held in the MOHC tape archive. The
proposed interface will be based on archives at BADC and MOHC using a common Data Reference Syntax (DRS) access
mechanism that allows flexibility for project specific referencing. This will allow the interface to be used for
routine delivery of climate data for model intercomparison projects through archive synchronisation and ultimately
remote access to approved sections of the MOHC archive for users of the BADC.
\par \vspace{2mm}
The use of a common DRS structure will support long-term integration into the ESGF infrastructure as this matures. The
proposed architectural solution deals with common archive lifecycle scenarios including upload, redaction, version
update etc. JMS messaging will be used to notify the BADC systems of changes in the MOHC archive status. MOHC will
develop a wrapper around its general purpose archive access tool to support BADC access.
\par \vspace{2mm}
The architectural design for the interface has been documented and accepted by both BADC and MOHC.
\subsection{Future work}
Work will now move to the detailed design and implementation work for the archive interface. This will include early
testing of the technologies identified in the architectural design. The implementation work will be undertaken by a
joint BADC and MOHC development team. The interface will be released in a phased process over the next 12 months with
increasing functionality at each release.
 
\end{document}
